---
title: "In Class Lab - DIY Functions"
author: "Precious Merenu"
date: "DATA 2401"
output: html_document
---
**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity 
The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time. 

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celcius equivalent. 

```{R}
celcius = function(fahrenheit){
  answer = (5/9) * (fahrenheit - 32)
  answer 
}
 present_answer = celcius(52)
 print(paste(present_answer, "degrees celcius."))
 

```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r}

celcius_meters = function(fahrenheit, inches){
  cel_answer = (5/9) * (fahrenheit - 32)
  meters_answer = inches * 0.0254
  return(list(celcius = cel_answer, meters = meters_answer))
  
}
 present_answer = celcius_meters(52, 6)
 
 print(paste(present_answer$celcius, "degrees celcius."))
 print(paste(present_answer$meters, "degrees celcius."))


```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R}
pos_or_neg = function(num)
{
  if (num > 0) 
    {
  print("The answer you have entered is positive. Great job!")
    }
 else if (num < 0)
    {
  print("The answer you have entered is negative. Great job!")
    }
  else
   {
    print("The answer you have entered is zero. Great job!")
   }
}
present_answer = pos_or_neg(0)

```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r}
find_absolute_val = function(num)
  {
  if (num > 0) 
    {
  print(paste("The absolute value of the number is: ", num, ". Great job!"))
    }
 else if (num < 0)
    {
  print(paste("The absolute value of the number is: ", (num/-1), ". Great job!"))
    }
  else
   {
    print("The answer you have entered is zero and doesn't have an absolute value. Great job!")
   }
}
  
  present_answer= find_absolute_val(-5)

```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r}
find_absolute_val = function(num)
  {
  if (is.numeric(num) == TRUE)
    {
  print(paste("Error!! Please pass a numerical value to this function. Try Again. "))
    }
  else if (is.character(num) == TRUE)
    {
  print(paste("Error!! Please pass a numerical value to this function. Try Again. "))
    }
  else if (num > 0) 
    {
  print(paste("The absolute value of the number is: ", num, ". Great job!"))
    }
 else if (num < 0)
    {
  print(paste("The absolute value of the number is: ", (num/-1), ". Great job!"))
    }
  else
   {
    print("The answer you have entered is zero and doesn't have an absolute value. Great job!")
   }
}
  
  present_answer= find_absolute_val("s")


```
   
   






```

